---
title: "IntroMarkDown"
author: "Viraj @DataTasteMaker"
date: "March 19, 2016"
output: 
  pdf_document: 
    toc: yes
---

##  Introduction to Markdown through Class Assignment  
Using the Basic of R, we can see how to create R-Markdown file. This is useful to document your code for future reference. It is intersting and also very easy to use.  

##  Remove/clear the memory  
Always clear the R-Environment and plots history before starting with any new code/script. This helps freeing up the memory which otherwise is unnecessarily blocked my the R-objects.

```{r, echo=FALSE}
rm(list = ls())  # clears/removes all the objects, lists, vectors, data frames, etc.
dev.off()        # Clears/closes all the graphic devices, and plot window
```

## Load libraries if any  
Always have the list of libraries to be included at the start of your script. Also if possible do make a reference as to why you are including/loading this library.  
```{r}
library(psych)  # for the use of "describe()" function to get the summary statistics.
```
***  

## 1. Create a vector of length 12. Print the 3rd and 7th element
```{r}
vec12 <- seq(1,12)
vec12
vec12[c(3,7)]
```

## 2. Create a vector of lenth 21 stating with the value 3.4 and ending with value 9.6.

```{r}
vec2 <- seq(3.4,9.6, length.out = 32 )
vec2
```
**What is the position of value 8.0?**

```{r}
which(vec2 == 8.0)
```

## 3. Create the 4x4 matrix

```{r}
m <- matrix(c(1,3,4,2,6,2,12,9,3,7,8,9,2,1,8,0), byrow = T, nrow = 4)
m
```
** 3a. Return 2nd column of the matrix**

```{r}
m[,2]
```
**3b. Change the element in the 2nd row and 2nd col to 3**
**Element in 2nd row and 2nd col -- Before**
```{r}
m[2,2]
```
**Element in 2nd row and 2nd col -- After**

```{r}
m[2,2] <- 3
m[2,2]
```

## 4. Randomly sample and form a vector of length = 200 and mean = 4 and std.dev =2.
**Use set.seed(100)**

```{r}
set.seed(100)
r200 <- rnorm(200, mean = 4, sd = 2)
head(r200)
tail(r200)
```

## 4a. Total Values less than 2.

```{r}
sum(r200 < 2)
```

## 4b. Total values between 3 and 5 (excluding 3 and 5)

```{r}
sum(r200 > 3 & r200 <5)
```

## 4c. The mean and std. dev of the data

```{r}
mean(r200)
sd(r200)
```

## 5a Read the day1_data.csv file

```{r}
day1data <- read.csv("./datasets/IntroMarkdown_Data.csv", header = T) 
head(day1data)
```
**Dimension of the data file read in**

```{r}
dim(day1data)
```
***Mean, Std. dev., Min and Max of column 4 i.e. X4**

```{r}
mean(day1data$X4, na.rm = T)
sd(day1data$X4, na.rm = T)
min(day1data$X4, na.rm = T)
max(day1data$X4, na.rm = T)
```
** Alternate way - using describe from `*psych*` library**

```{r}
describe(day1data$X4, na.rm = T)
```
