---
title: "kmeans_with_prediction"
author: "Viraj @DataTasteMaker"
date: "March 29, 2016"
output: pdf_document
---

k-means clustering and predicting:

**Clear memory**
```{r}
rm(list=  ls())
```

**Load *iris* data**

```{r}
set.seed(1) # to get same output everytime
ipdata <- iris[,-5]
head(ipdata)
```
```{r,echo=FALSE}
cat("Original iris data")
head(iris)
```

**Run k-means with 3 clusters as *iris* data has 3 segments**
```{r}
km <- kmeans(ipdata,3)
```

**See how the means/centers are for each cluster**
```{r}
km$centers
```

**Create a list of new values to predict**
```{r}
# new data record values
myvalues <- c(5.1,3.5,1.4,0.2) # here I have used the first record values
```

**now extract mean values for each cluster, then find the Euclidean distance of each values with the new values**
```{r}
model_cluster1 <- km$centers[1,]
model_cluster2 <- km$centers[2,]
model_cluster3 <- km$centers[3,]

ed_cluster1 <- sqrt(sum((model_cluster1 - myvalues)^2))
ed_cluster2 <- sqrt(sum((model_cluster2 - myvalues)^2))
ed_cluster3 <- sqrt(sum((model_cluster3 - myvalues)^2))
```

**The distances for each clusters are as below**
```{r}
cat("The distances are", ed_cluster1, ed_cluster2, ed_cluster3)
```

**Now find the minimum value of the 3 distances, the one with the minimum value is the cluster this new data will be falling into**
```{r}
cat("The new record withe values -->", myvalues, " will fall into cluster# = ",
which.min(as.list(c(ed_cluster1,ed_cluster2,ed_cluster3))))
```

**To cross validate our model we can do it as below**
```{r}
## As I had pulled the first record of the data file, let's see which segment it was marked in

iris[1,]
## as you see the cluster it is marked in is "setosa"
## and as per the table below, the kmeans model is setting Cluster 1 as Setosa
table(iris$Species,km$cluster)
plot(ipdata[c(1:2)], col=km$cluster, pch=19)
```







