---
title: "WordCloud"
author: "Viraj @DataTasteMaker"
date: "March 28, 2016"
output: pdf_document
---

This script creates a word cloud, by reading the CSV file which has words and its frequencies as per the requirement.

The script is not actually reading any text, to extract the words and the frequency of those words, instead that info is manually entered in the *"wrdCloud_data.csv"* file.

This *"wrdCloud_data.csv"* file is then read in and the names and frequencies are passed to the wordcloud function to generate the requried image.


**Always clear the environment and plots to free up the memory, before starting.**
```{r, echo=FALSE}
rm(list = ls())
dev.off()
```


**Load the required libraries, you might have to install them if not already**
```{r}
library(RColorBrewer) # This is required for wordcloud library
library(wordcloud)
```


**Read the CSV file and view the data if all corret**
```{r, echo=FALSE}
wrdCloud  <- read.csv("./datasets/wrdCloud_data.csv", sep = ",")
wrdCloud[,c(1:10)]
```

**Now call the wordcloud function and pass the data frame and other parameters**
```{r}
wordcloud(
  names(wrdCloud), wrdCloud, min.freq = 10,
  colors = brewer.pal(8, "Set1"),scale = c(1.7, 0.1)
)
```

